Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2016-03-15 Reviews/response.tex

\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{amsmath}

\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}

@@

\begin{quote}
    \begin{textit}
        {
        In Figure 7, the caption should state which points are \(f_NH\) and
        which are \(F_RG\).
        }
    \end{textit}
\end{quote}

This is a good point, we have clarified this by noting `crosses' and `diamonds' in plain text in the caption.

\begin{quote}
    \begin{textit}
        {
I was puzzled as to whether the target, t, appeared in the definition
of \(T^*\). As I understand it, \(T^*\) is independent of \(t\). Is this true?
Also, for which values of \(K_{NH}\) and \(K_{RG}\) is the maximum achieved? Is my
intuition correct that it is achieved at \(K_{NH} = c_{NH}\) and \(K_{RG} = c_{RG}\)?
        }
    \end{textit}
\end{quote}

This is an excellent question. The reviewer understand correctly: \(T^*\) is
not dependent of \(t\).

Identifying the point at which throughput is maximised is however not
immediate. When we began working on this paper we had the same intuition as the
reviewer (that throughput would always be maximised when using the highest
possible threshold), however this is not the case.

Indeed, for example for the second model, when using a system with parameters:

\begin{itemize}
    \item \(c_{\text{RG}}=2, c_{\text{NH}}=3\)
    \item \(\mu_{\text{RG}}=0.22, \mu_{\text{NH}}=1.66\)
    \item \(\lambda_{\text{RG}}=3, \mu_{\text{NH}}=1\)
\end{itemize}

The throughputs for each cutoff pair are shown in the table below:

\begin{center}
    \begin{tabular}{cc}
        \toprule
        Throughput & Cut off pairs\\
        \midrule
        1.704098 &(2, 0)\\
        1.843005 &(1, 0)\\
        1.857689 &(0, 0)\\
        3.27514 &(2, 1)\\
        3.472371 &(1, 1)\\
        3.51033 &(0, 1)\\
        4.291777 &(2, 2)\\
        4.488501 &(1, 2)\\
        4.549065 &(0, 2)\\
        4.767654 &(2, 3)\\
        4.877357 &(1, 3)\\
        4.916791 &(0, 3)\\
        4.928235 &(2, 4)\\
        4.961882 &(1, 4)\\
        4.969698 &(0, 4)\\
        \bottomrule
    \end{tabular}
\end{center}

We see that the optimal throughput is obtained when RG is in effect `closed'
and NH is never in a diverted state. This is due to the fact that the service
rate for RG is very low and NH is not subject to high levels of demand. Through our investigations other examples occur that evidence this: the main idea that seems to pervade is that running a system at full capacity is not necessariy optimal.

If it is of interest the Sagemath code (making use of the models distributed
with the previously made available code) to obtain the above table is:

\begin{minted}[frame=lines]{python}
capacity_list = [2, 3]
serviceratelist = [0.22, 1.66]
demandratelist = [3, 1]
model = Model2(capacity_list, serviceratelist, demandratelist)
model.sweepcutoffs()
tps = {model.data[pair].throughput1 + model.data[pair].throughput2: pair for pair in model.data}
for tp in sorted(tps.keys()):
    print round(tp,6), tps[tp]
\end{minted}

A brief discussion of this has been added to the paper which now reads:

... This optimal throughput \(T^*\) is
independent of \(t\).

Note that intuitively it could be thought that \(T^*\) is obtained when
\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
(numerical experiments have been carried out to verify this).

### 2016-03-15 Paper/paper.tex
Adding discussion about optimal T^*.

We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of (\ref{model1}) (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.

>>>>

We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium
obtained by solving the game of (\ref{model1}) (in case of multiple equilibria
we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{\NH},
K_{\RG}}\left(T_{\NH}+T_{\RG}\right)$. This optimal throughput \(T^*\) is
independent of \(t\).

Note that intuitively it could be thought that \(T^*\) is obtained when
\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
(very numerical experiments have been carried out to verify this).
